Elite individuals, insitutions, and economic growth accounting

### 2024-04-11 presentation/main.tex
should be done

\begin{frame}{Limitations: data problems}
    Regression results do not present a clear picture of the existence of a statistical relationship between elite indicators and economic growth.
    \begin{block}{Little variation in data}
        \begin{itemize}
            \item Countries and regions with PISA test scores tend to be wealthier, more developed economies
            \item Low variance within countries over time and between countries as a result
        \end{itemize}
    \end{block}

    \begin{block}{Model specification matters}
        \begin{itemize}
            \item Including entity fixed effects a significant difference versus time effects (likely due to above)
            \item Large variation in $IMO, math99$ between time effects, fixed effects, panel models
            \item Missing data (only post-2006 EIU Democracy index scores, missing school completion rates)
            \begin{itemize}
                \item XGBoost is used to fill in this data as controls are somewhat stable year-to-year, but this is not perfect
            \end{itemize}
        \end{itemize}

    \end{block}

@@

\begin{frame}{Limitations: Yearly vs. Panel}{Significant year-to-year variation}
    \begin{block}{Unstable panel vs. yearly results}
        The panel methods mask some of the year-to-year changes in relationships.
        Some indicators are more stable than others, but $math99$ in particular alternates from positive to negative coefficient with large swings.
    \end{block}

@@

>>>>

\begin{frame}{Limitations}
    Regression results do not present a clear picture of the existence of a statistical relationship between elite indicators and economic growth.
    \begin{block}{Little variation in data}
        \begin{itemize}
            \item Countries and regions with PISA test scores tend to be wealthier, more developed economies
            \item Low variance within countries over time and between countries as a result
        \end{itemize}
    \end{block}

    \begin{block}{Missing data}
        \begin{itemize}
            \item XGBoost imputation is not perfect and it may have introduced bias
        \end{itemize}
    \end{block}

    \begin{block}{Reverse causality and timelines}
        \begin{itemize}
            \item Countries which grow faster may try and solidify the growth by pushing for academic exellence
            \item Lagged regression should be considered; it is not clear elite students in time $t$ have an immediate effect
        \end{itemize}
    \end{block}

@@

\begin{frame}{Limitations}{Regression framework concerns}
    \begin{block}{Unstable panel compared to yearly results}
        The panel methods mask some of the year-to-year changes in relationships.
    \end{block}

@@

    \begin{block}{Heterogeneity}
        No time for this today, but I have other models which include interactions to examine this. Highly possible richer/poorer countries experience different effects.
    \end{block}
